Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-14 paper/ms.tex
moved sturm's theorem to appendix

\subsection{Ensuring positive definiteness: Sturm's theorem}

A procedure based upon Sturm's theorem \citep{Dorrie:1965} allows one to determine whether there are any
real roots within the range $(0,\infty]$. We first construct $P_0(z)$ and it's derivative
$P_1(z) = P^\prime(z)$, and then loop from $k=2$ to $k=p_{ord}$, computing
$P_k(z) = -{\rm rem}(P_{k-2},P_{k-1})$.  The function ${\rm rem}(p,q)$ is the remainder polynomial after dividing $p(z)$ by $q(z)$.

The advantage of this procedure is that it does not require computing the roots, but only carrying out algebraic
manipulation of polynomials to determine the number of positive real roots.  If a non-zero real root is found, then
likelihood may be set to zero.
%Sturm's theorem applied to numerator of power spectrum.

@@

>>>>

@@

\appendix

\section{Ensuring positive definiteness: Sturm's theorem}

For arbitrary $J$, a procedure based upon Sturm's theorem \citep{Dorrie:1965} allows one to determine whether there are any
real roots within the range $(0,\infty]$. We first construct $P_0(z)$ and it's derivative
$P_1(z) = P^\prime(z)$, and then loop from $k=2$ to $k=p_{ord}$, computing
$P_k(z) = -{\rm rem}(P_{k-2},P_{k-1})$.  The function ${\rm rem}(p,q)$ is the remainder polynomial after dividing $p(z)$ by $q(z)$.

The advantage of this procedure is that it does not require computing the roots, but only carrying out algebraic
manipulation of polynomials to determine the number of positive real roots.  If a non-zero real root is found, then
likelihood may be set to zero.

We have implemented this algorithm in subroutines that may be called to check for positive-definiteness
of a kernel with some values of $a_j$ or $b_j$ negative.
%Sturm's theorem applied to numerator of power spectrum.
